Model Samples Processing

### 2020-01-22 stats/model_sample_processing.Rmd
add model with RE

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)
library(langcog)

>>>>

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)
